Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-06-04 index.Rmd
Finish adapting old content and improve outline

@@

* P1: Wide range of dependence, allowing both positive and negative dependence
* P2: Flexible dependence, meaning that the number of bivariate marginals is (approximately) equal to the number of dependence parameters.
* P3: Flexible marginal modeling, generating hetereogenous data --- possibly from differing probability families.
* P4: Computationally feasible cumulative distribution function (cdf) for likelihood estimation.

Moreover, in simulation method must scale to high dimensions:

@@

# Multivariate correlation bounds

# Simulation methodology

## General algorithm

## Rank-based dependence measures

## Pearson correlation

Difficulties

@@

```{r setup, eval=TRUE}
## Using conda
reticulate::use_condaenv("py37")
library(bigsimr)
```

@@

## Comparsions to other software

### Speed

- `copula`
- `Genord`
- `Multiord`
- other?
- CPU benchmarking
- GPU benchmarking

### Accuracy

blah

### Other comparisons

blah

@@

## Simulation-based correlation checking

A multivariate approach?

Or all the pairs?

Generate, sort, and correlate algorithm @Demirtas2011

```{r, computeFrechetBounds, echo = TRUE, eval=TRUE}

@@

margins2 <- list(
    list("nbinom", 5, 0.3),
    list("exp", 4),
    list("binom", 5, 0.7),
    list("norm", 10, 3),
    list("pois", 10)
)

@@

## help(package="bigsimr")
rho_bounds <- computeCorBounds(params = margins, cores = cores, type = "spearman", reps = reps)
rho_bounds
```

## Simulating RNA-seq data

## Simulation-based correlation testing

## Simulation-based probability calculations

@@

# Conclusions

>>>>

## Ultra High Dimensional multivariate modeling and simulation desired properties

@@

* P1: Wide range of dependence, allowing both positive and negative dependence
* P2: Flexible dependence, meaning that the number of bivariate marginals is (approximately) equal to the number of dependence parameters.
* P3: Flexible marginal modeling, generating hetereogenous data --- possibly from differing probability families.

Moreover, the simulation method must scale to high dimensions:

@@

# Background and notation

## Gaussian copulas

We present an general-purpose, scalable multivaritae simulation algorithm. The crux of the method is construction of a Gaussian copula. This idea is well known [refs]. A copula is a distribution function on $[0,1]^d$ describing a random vector with standard uniform marginals. Moreover, for any random vector ${\bf X}=(X_1, \ldots, X_d)$ with cumulative distribution function (CDF) $F$ and marginal CDFs $F_i$ there is a copula function 
$C(u_1, \ldots, u_d)$ so that

\[
F(x_1, \ldots,x_d) = \mathbb P(X_1\leq x_1, \ldots,X_d\leq x_d) = C(F_1(x_1), \ldots, F_d(x_d)), \,\,\, x_i\in \mathbb R, i=1,\ldots,d. 
\]

A Gaussian copula is the case where all marginal CDFs $F_i$ are the standard normal cdf, $\Phi$. The Gaussian copula is the one that corresponds to a multivariate normal distribution with standard normal marginal distributions and covariance matrix ${\bf R}$. (Since the marginals are standard normal, this ${\bf R}$ is also the correlation matrix). If $F_{{\bf R}}$ is the CDF of such multivariate normal distribution, then the corresponding Gaussian copula $C_{{\bf R}}$ is defined through

\begin{equation}
(\#eq:gauss)
F_{{\bf R}}(x_1, \ldots, x_d) = C_{{\bf R}}(\Phi(x_1), \ldots, \Phi(x_d)),
\end{equation}

where $\Phi(\cdot)$ is the standard normal CDF. Note that the copula $C_{{\bf R}}$ is simply the CDF of the random vector $(\Phi(X_1), \ldots, \Phi(X_d))$, where  $(X_1, \ldots, X_d) \sim N_d({\bf 0}, {\bf R})$.

Sklar's Theorem (ref) guarantee's that any random vector with computational feasible inverse CDFs (P4 above) and obtainable correlation matrix (within the Frechet bounds) can be obtained via transformations involving copula functions. Namely, to simulate a random vector ${\bf Y}  = (Y_1, \ldots,  Y_d)$, where $Y_i=F_i^{-1}(U_i)$, $i=1, \ldots, d$, we can construct a Gaussian copula ${\bf U} = (U_1, \ldots,  U_d)$ viz $U_i=\Phi(X_i)$, $i=1, \ldots, d$. When an $Y_i$ is discrete, some care must be taken to define $F_i$. Letting

\begin{equation}
F_{i}^{-1} = inf\{y:F_{i}(y) \geq u \}
(\#eq:inverseCDF)
\end{equation}

\noindent ensures that $Y_i \sim F_i$.

Simulation of a general multivariate random vector ${\bf T}$ with margins $F_i$ based on this copula is quite simple. Ensuring that one obtains a certian dependence among the marginal distributions, however, proves challenging in our proposed Gaussian-copula-based scheme. Two core issues: 1) marginal characteristics induce bounds on the possible bivariate correlations and 2) montone transformations deform the Pearson correlation which no closed form expression exists in general (ref? Chen2001). The Frechet bounds are well-known.

## Measures of dependency

The population correlation coefficient, commonly called the Pearson (product-moment) correlation coefficient, describes the linear association between two random variables $X$ and $Y$ and is given by

\begin{equation}
(\#eq:pearson)
\rho(X,Y) = \frac{E(XY) - E(X)E(Y)}{\left[ var(X)var(Y)\right]^{1/2}} 
\end{equation}

As @MB13 and @MK01 discuss, for a bivariate normal $(X,Y)$ random vector the Pearson correlation adequately describes the dependency between the components. $\rho$'s utility in non-normal or non-linear associations is lacking (@MK01). Rank-based (ordinal) approaches performance better in these settings, such as Spearman's (denoted $\rho_s$) and Kendall's $\tau$. Define

\begin{equation}
(\#eq:spearman)
\rho_s(X,Y) = 3 \left[ P\left[ (X_1 - X_2)(Y_1-Y_3) > 0 \right] - P\left[ (X_1 - X_2)(Y_1-Y_3) < 0 \right] \right]
\end{equation}

\noindent where $(X_1, Y_1) \overset{d}{=} (X,Y), X_2 \overset{d}{=} X, Y_3 \overset{d}{=} Y$ with $X_2$ and $Y_3$ are independent of one other and of $(X_1, Y_1)$. For continuous marginals, the measure works well due to zero probability of ties. For discrete marginals, however, one could perform a rescaled version of $\rho_s$ for random variables $X,Y$ with pmfs (or pdfs) $p(x)$ and $q(y)$, respectively.

\begin{equation}
(\#eq:spearmanRescaled)
\rho_{RS}(X,Y) = \frac{\rho_s(X,Y)}{ \left[ \left[ 1 - \sum_x p(x)^3 \right] \left[ 1 - \sum_y q(y)^3 \right] \right]^{1/2}}
\end{equation}

\noindent Kendall's $\tau$ is the probability of concordant pairs minus the probability of discordant pairs and is given compactly as

\begin{equation}
  (\#eq:tau)
  \tau(X,Y) = \frac{\rho_s(X,Y)}{ \left[ \left[ 1 - \sum_x p(x)^3 \right] \left[ 1 - \sum_y q(y)^3 \right] \right]^{1/2}}
\end{equation}

## Marginal-dependent bivariate correlation bounds

The pairwise correlation between two correlated random variables cannot in general obtain the full range of possibile values, $[-1,-1]$. The range, called the Frechet(-Hoeffding) bounds, is a well-known function of the marginal distributions and are given by [@BF17]:

\begin{equation}
(\#eq:frechet)
\rho^{max} = \rho \left( F^{-1}_1 (U), F^{-1}_2 (U) \right), \quad \rho^{min} = \rho \left( F^{-1}_1 (U), F^{-1}_2 (1 - U) \right)
\end{equation}

\noindent where $U$ is a uniform random variable in $(0,1)$, and $F^{-1}_1, F^{-1}_2$ are the inverse cdf of random variables $X_1$ and $X_2$, respectively. For discrete random variables, define $F^{-1}$ as in Equation \@ref(eq:inverseCDF).

# Simulation algorithm

## Algorithm description

This section describes the method for simulating a random vector $\bf Y$ with $Y_i$ components for $i=1,2,\ldots,d$. Each $Y_i$ has a specified marginal
distribution function $F_i$ and its inverse. To characterize dependency, every pair $(Y_i, Y_j)$ has either a specified Pearson correlation \@ref(eq:pearson), (rescaled) Spearman correlation \@ref(eq:spearmanRescaled) , or Kendall's $\tau$ (Equation \@ref(eq:tau) ). The method only approximately matches the Pearson correlation in general, whereas the rank-based methods are exact.

The method is best understand as a **parallelized Gaussian copula** (see Equation \@ref(eq:gauss). We shall see that contructing continuous joint distributions that match a target Spearman or Kendall's correlations computes easily when employing Gaussian copulas, since this measures are invariant under the monotone transformations involved [refs]. To do this, we take advantage of a closed form relationship [ref?] between Kendall's $\tau$ and Pearson's correlation coefficient for bivariate normal random variables:

\begin{equation}
(\#eq:convertKendall)
r_{Pearson} = sin \left( \tau_{Kendall} \times \frac{\pi}{2} \right), 
\end{equation}

\noindent and similarly for Spearman's $\rho$ [@K58],

\begin{equation}
(\#eq:convertSpearman)
\rho_{Pearson} = 2 \times sin \left( \rho_{Spearman} \times \frac{\pi}{6} \right).
\end{equation}

For discrete marginals, achieving a target Spearman correlation under this scheme is possible by using components rom Equation \@ref(eq:spearmanRescaled) to further adjust the input correlation matrix. Let the unscaled Spearman correlation coefficients be $\rho_{s} \left(Y_{i}, Y_{i^\prime}\right)$ for two marginal distributions and divide the target correlation by the product in the denominator of Equation \@ref(eq:spearmanRescaled). Let these adjustment factors be denoted as $a_i = \left[ 1 - \sum_y p_i(y)^3 \right]^{1/2}$ and specifically rescale the target Spearman correlation matrix by

\begin{equation}
(\#eq:convertSpearmanDiscrete)
\rho_{rs} \left(Y_{i}, Y_{i^\prime}\right) = \frac{\rho_{s} \left(Y_{i}, Y_{i^\prime}\right)}{a_i \times a_{i^\prime}}.
\end{equation}

In a similiar fashion, we rescale Kendall's $\tau$ to adjust the input correlation matrix. The conversion formula is given by

\begin{equation}
(\#eq:convertKendallDiscrete)
\rho_{rs} \left(Y_{i}, Y_{i^\prime}\right) = \frac{\rho_{s} \left(Y_{i}, Y_{i^\prime}\right)}{a_i \times a_{i^\prime}}.
\end{equation}

In contrast the rank-based correlations, matching specified Pearson correlation coefficients exactly is computational intense in this scheme. In general, there is no closed form correspondence and involving computing or approximating $\binom{d}{2}$ integrals of the form $EY_iY_j = \int \int y_i y_j f_{X|r}(F_i^{-1}(\Phi(z_i)), F_j^{-1}(\Phi(z_j))dy_idy_j$, for $i,j=1,2,\ldots,d$. For accurate numeric approximation of these integrals, the functions must be evaluated hundreds of times. Others have used efficient Monte Carlo integration schemes (see @Chen2001), but scale poorly to large dimension in reasonable times (property **S2**). Despite all this, if one does desire to characterize dependency using Pearson correlations, we often see in practice --- and it is theoretically justified under certain conditions (@Song00) --- that simply using the target Pearson correlation matrix as the initial conditions to our proposed algorithm will lead to approximate matching in the resultant distribution.

## Simulation Algorithm

Putting the together the facts provided in the equations above, we come the following proposed simulation algorithm to produce a random vector ${\bf Y}$ with specified Spearman's correlation and marginal distributions. Note that all computational steps can be parallelized as each operation can be done or either the $d$ marginals or the $\binom{d}{2}$ pairs for the correlation values. Even the generation of multivariate normal random vectors is parallelized through optimized matrix multiplication/decomposition routines.

### Inputs
(1) Marginal characteristics including the same of distributional family and parameter values, denotes as $F_i$ for marginal component random variable $Y_i$ for $i=1,\ldots,d$.
(2) A target (specified) Spearman's correlation matrix ${\bf R_{Spearman}}$ with
each $\rho_{Spearman}$ within the Frechet limits. Alternatively, the rescaled
Spearman's correlation (see Equation \@ref(eq:convertKendallDiscrete) ) can be provided.
(3) An error tolerance $\epsilon$ for finding the nearest positive definite matrix a transformed correlation matrix (see step iii below). Alternatively, a maximum number of iterations can be supplied.

### Algorithm
(i) Compute Spearman's $\rho_{rs}$ (see Equation
\@ref(eq:convertKendallDiscrete)) from the specified $\rho_{spearman}$ for each
pair of marginal random variables $(Y_i,Y_{i^\prime})$ with $i \neq i^\prime$
when either marginal is discrete. In such large scale computations, it may be
that numerically $\rho_{rs}$ is be larger/smaller than the Frechet bounds (or
even $\pm 1$). To guard aganist this, set $\rho_{rs} = min( \rho_{rs}, M)$,
where $M$ is the upper Frechet bound (see [Section Introduction]) and similarly set $\rho_{rs} = max( \rho_{rs}, W)$, where $W$ is the lower Frechet bound for this pair of distributions. Gather these $\rho_{rs} \lq s$ into a new input correlation matrix ${\bf R_{rs}}$.  
(ii) Convert ${\bf R_{Spearman}}$ into ${\bf R_{Pearson}}$ via $\rho_{Pearson} = 2 \times sin \left( \rho_{rs} \times \frac{\pi}{6} \right)$.   
(iii) Finally, ensure that ${\bf R_{Pearson}}$ is positive definite, by finding the nearest positive definite correlation matrix ${\bf R}$ --- using the `R` routine `nearPD` in the `Matrix` package --- within an error tolerance of $\epsilon$.  
(iv) Generate ${\bf X}=(X_1, \ldots, X_d) \sim N_d({\bf 0}, {\bf R})$;  
(v) Transform ${\bf X}$ to ${\bf U} = (U_1, \ldots,  U_d)$ viz $U_i=\Phi(X_i)$, $i=1, \ldots, d$;  
(vi) Return ${\bf Y}  = (Y_1, \ldots,  Y_d)$, where $Y_i=F_i^{-1}(U_i)$, $i=1, \ldots, d$;

@@

The most computationally extensive lies in the second step of our algorithm. We
use a optimized and parallelized multivariate normal simulator within the `R`
package `mvnfast`. The rest of the code is also parallelized, but these steps
run rapidly in serial computation except for extremely large dimension.

```{r setup, eval=TRUE}
## Using conda
reticulate::use_condaenv("py37")
library(bigsimr)
## help(package = 'bigsimr')
```

@@

# Monte Carlo evaluation and Comparsions to other software

Before applying our methodology to real data simulation, we conduct several Monte Carlo studies to investigate method performance in comparison to other existing implementations. We focus the numerical experiments on assessing how well the procedure scales to high dimension with respect to reasonable computation times (property S1 above) and accurately matching marginal and dependency paramaters. The simulations will proceed in increasing complexity --- leading up to the setting in our motivating example. We begin by exploring simple exchangeable (constant) correlation structures under a large number of simulation replicates while applying the algorithm above to first continous then discrete marginal distributions. We conclude the simulation studies with $10^5$ replicated data sets with sample sizes and distributional characteristics corresponding the estimates from the motivating example data.

The CPU-based computation times we report were from runs using eight dual-threaded 3.9GHz
Xeon Gold processors on a linux workstation, allowing for parallel instructions
over 16 cores. We choos 15 cores for our experiments.

## Other multivariate simulation software

Describe the competing software and algorithms briefly.

- `copula`
- `Genord`
- `Multiord`
- `nortaRA` only does Pearson matching.

## Simulation I: Bivariate simulation using rank-based correlation

### Continuous example: Bivariate Exponential

Both Spearman's and Kendall's measures of dependency are invariant under
strictly monotone transformations (ref). This in turn provides exact simulation
of continuos marginals $F_i$ $i=1,\ldots,d$ since their corresponding quantile
function are increasing montonically over their support. The results below
provide computations times for $N=10^5$ under increasingly large dimension $d$.
For simplicity we assume multivariate Normal with varying parameters and to
additionally demonstrate the utility of Kendall's $\tau$ even in the Gaussian
setting (as opposed to the nature choice of Pearson's correlation). To layer on complexity, we now assume a multivariate gamma distribution with fixed marginal parameters.

Compare speed and accuracy.

```{r tabGamma, echo = TRUE}
## computation times normal

```
### Discrete example: Bivariate Geometric

Compare speed and accuracy.

## Simulation II: Ultra HD multivariate simulation with identical margins and exchangeable rank-based correlation.

### UHD Continuous example: Multivariate Gamma

Compare speed and accuracy.

### UHD Discrete example: Multivariate Negative Binomial

Compare speed and accuracy.

## Simulation III: Ultra HD multivariate simulatino with heterogenous margins and exchangeable rank-based correlation.

### UHD Heteregeous continuous example: Multivariate Gamma

Compare speed and accuracy.

### UHD Heteregeousdiscrete example: Multivariate Negative Binomial

Compare speed and accuracy.

@@

## Simulating Ultra High Dimensional RNA-seq data

```{r brca, echo=TRUE, eval=FALSE}
## full workflow simulating RNA-seq data

```

The data are overdispersed:

```{r figNBratio, echo = FALSE, eval=FALSE, message=FALSE, warning=FALSE, fig.path='fig/plot-', out.width= '75%', fig.align='center', fig.ext='pdf', fig.cap="The genes display extreme overdispersion. Using group-specific sample means and variances for each of the d=4777 genes, we display the distributions oflog of variance to mean ratio (log(sigma2/mu))."}
## http://www.sthda.com/english/wiki/ggplot2-histogram-easy-histogram-graph-with-ggplot2-r-package
## devtools::install_github("kassambara/easyGgplot2")
library(easyGgplot2)
## p0 <- ggplot(data = nb_dat, aes(x = log(nb_var / nb_mean), y = stat(density), fill=group))
## p0 + geom_histogram(bins = 30) + labs(x="log of variance to mean ratio") + theme_bw()
nb_dat$logRatio <- log(nb_dat$nb_var / nb_dat$nb_mean)
ggplot2.histogram(data=nb_dat, xName='logRatio',
    groupName='group', legendPosition="right",
    alpha=0.5, addDensity=TRUE,
    addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5)
```

We see that the all genes studies display overdispersion (variance greater than mean) compared to a Poisson model for the gene counts. The genes are highly hetereogeneous even when dealing with highly expressed genes after filtering. The facts taken together motivate the negative binomial model for the marginal distributions. The genes are slightly more variable within the deceased group (expected with smaller sample size and potentially due to biomedical considerations).

Next we perform some essential pre-processing of the data. Since our goal is to simulate meaningful multivariate constructions, we must first find a subset of 20501 genes that are expressed. In order words, we'll filter out the low expressing genes to allow greater range of possible $d$-variate correlations (see @NK10 for details OR SHOULD I EXPLAIN THIS MORE CAREFULLY?). Notably, many RNA-seq analytic workflows filter out low expressing genes (see \cite{Conesa2016b}) and this, admittedly, is usually done in an \emph {ad hoc} fashion. In this study, we prefer an inclusion criterion that is theoretically motivated. Based on the results in Section BLAH, we filter genes with a sample mean less than 12. In this way, we remove 4762 (23.2\%) of the genes, retaining 15,739 genes for further analysis. The filtered low-expressing genes will be simulated as independent negative binomial random variables to form a complete simulated transcriptome.

RNA-sequencing data derived from breast cancer patients (n=1093), with 20501 genes measured (from TCGA). We filter to genes with average expression greater than 10000 counts (d = 4777) across both groups. Consider basic differentially expressed genes (DEG) analysis between surviving (n0 = 941) and deceased (n1 = 152) patients. This setting can be described as large-scale simultaneous hypothesis testing, under correlation. We should evaluate existing and new methodology using simulations that reflect dependency among variables. But multivariate simulation tools often scale Tpoorly to high dimension or do not model the full range of dependency. Perform a two-sample $t$ test for each 4777 genes on the observed RNA-seq counts ($empirical$). Call a "Z score" for the $i^{th}$ gene $Z_{i} = \Phi^{-1}(t_{\approx 272}(t_i))$.

Our method requires some measure of that the covariance structure is pre-specified. In practice, however, high-dimensional covariance estimation is not that easy. Indeed there is much recent interest in this area (cite a few recent high visibility articles --- see the GPU-NORTA pub). Here we do not provide a comprehensive review on the topic. Instead we only seek to use covariance estimator that only guarantees postive-semidefiniteness while maintaining adequate estimation properties. To this end we chose to use the condition-number-regularized (\textsc{condreg}) approach of \cite{Won2013g}. This covariance estimation procedure restricts the ratio of the largest eigenvalue to the smallest eigenvalue to improve numerical results. But the method employs a penalized Gaussian likelihood. And so, rather than estimating the covariance on the discrete counts directly, we first perform a $log_{2}(x +1)$ transformation to better suit this modeling assumption. \textsc{condreg} requires a parameter, $\kappa_{max}$, that controls the largest condition number of the resultant estimated covariance matrix. Here we aim to allow a large number of nonzero pairwise correlations and so arbitrary set $\kappa_{max}=10^{4}$. The routine ran without issue on a MacBook Pro carrying BLAH in XXX units of time.

Most pairwise correlations are nearly zero with XXX \% less than |0.1|. Yet there are dense subsets of correlated genes. And even small correlations among many variables can disrupt the operating characteristics of commonly used statistical inferential procedures \cite{Schissler2018}.

In this case study in the large-scale hypothesis testing in pursuit of detecting differentially expressed genes, we aim to simulate RNA-seq counts using a multivariate negative binomial. To evaluate the simulation's utility, we systematically compare the simulated results to the empirical results. In short we computed t-statistics and p-values for each of $d=4777$ genes between two groups of breast cancer patients (1=deceased, 0=alive; $n_0 = 152, n_1=941$). Further details on the empirical results are provided in Section BLAH. We compare two aspects in the simulation design 1) Choice of correlation measure while modeling marginal distributions consistently and 2) how well does the best-performing simulation agree with the empirical results. Informed by the simulation studies in Section BLAH, we anticipate a far amount of variation at such small sample sizes and large $d$ and so replicate the entire study 100 times.

To recap from the discussion above (Section BLAH), we estimated negative binomial parameters for each of the $d=4777$ genes and also their Pearson, Spearman, and Kendall's correlation coefficients from n=1093 breast cancer patients, within each vital status group (0=deceased, 1=alive). We generated 100 sythentic data sets for each group, with the number of $d$-dimensional random vectors produced equal to the corresponding sample sizes ($n_0 = 152, n_1=941$). These 100 samples are used to understand uncertainty in this setting and we will use the mean simulated values to compare to the empirical (and also explore the worst-case scenarios).

Model genes as marginally negative binomial with heterogenous genewise parameters. Compute sample correlations (using desired dependency measure) for the 11,407,476 genes pairs, for each group. To simulate gene expression counts, our goal is to produce a random vector ${\bf Y}=(Y_1, \ldots, Y_d)$ with **correlated** NB components. To do that, we start with a sequence of **independent** Poisson processes $N_i(t)$, $i=1,\ldots,d$, where the rate of the process $N_i(t)$ is $\lambda_i=(1-p_i)/p_i>0$ (so that $p_i=1/(1+\lambda_i)$). Now, we let ${\bf T} = (T_1, \ldots T_d)$ have a multivariate distribution on $\mathbb R_+^d$ with the PDF $f_{{\bf T}}({\bf t})$. Then, we define

We rescaled the target Spearman correlation to account for the probability of ties via Equation \@ref(eq:convertSpearmanDiscrete). The serial computation took approximately 10 minutes on XXX. Notably, the difference between target and adjusted matrices was very small (mean relative difference: 0.708) in this particular configuration of negative binomial parameters. For problems with smaller counts and higher probabilities of ties, the adjustment can be substantial (as observed in the simulation studies above in Section BLAH).

- Kendall's $\tau$ was estimated efficently using the `pcaPP::cor.fk` function in `R`.

## Ultra High-Dimensional simulation-based correlation hypothesis testing

```{r brcaSigmaTesting, echo=TRUE, eval=FALSE}
## full workflow simulating RNA-seq data

```

## Simulation-based computation of correlation bounds

Using the Generate, sort, and correlate algorithm @Demirtas2011

```{r, computeBounds, echo = TRUE, eval=FALSE}

@@

@@

## help(package="bigsimr")
rho_bounds <- computeCorBounds(params = margins, cores = cores, type = type, reps = reps)
rho_bounds
```

## Simulation-based joint probability calculations

```{r densityEvaluation, echo=TRUE, eval=FALSE}
## full workflow simulating RNA-seq data

```

@@
